---
title: "Final data cleaning"
author: "Anisha Dubhashi"
date: "11/19/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(lubridate)
```

###load data
```{r}
raw_data <- read_csv("catalog sales data.csv")
raw_data$datead6 <- as.Date(raw_data$datead6,format = "%m/%d/%Y")
raw_data$datelp6 <- as.Date(raw_data$datelp6,format = "%m/%d/%Y")

df <- raw_data
```

### Create year_ordyr
```{r}
df$year_ordyr <- 1980

#needs to be in order of least to most recent for overwriting
df$year_ordyr[df$ord3ago > 0] <- 2009
df$year_ordyr[df$ord2ago > 0] <- 2010
df$year_ordyr[df$ordlyr > 0] <- 2011
df$year_ordyr[df$ordtyr > 0] <- 2012
```

###Create recentseason function
```{r}
findSeason <- function(date, cutoff) {
  if (month(date) < cutoff) {
    season <- "Spring"
  }
  else {
    season <- "Fall"
  }
  return(season)
}
  
findSeasons <- function(dataframe, cutoff) {
  seasons <- sapply(dataframe$datelp6, findSeason, cutoff = cutoff)
  return(seasons)
}
```

### Create year_lp6yr
```{r}
df$recentseason <- findSeasons(df, cutoff = 7)

df$year_lp6yr <- year(df$datelp6)

# Jan-June of Year x -> fiscalyear.a = x
df$year_lp6yr[df$recentseason == "Spring"] <- year(df$datelp6[df$recentseason == "Spring"])

# July+ of Year x -> fiscalyear.b = x+1
df$year_lp6yr[df$recentseason == "Fall"] <- year(df$datelp6[df$recentseason == "Fall"]) + 1

#clean the 3 2013s
df$year_lp6yr[df$year_lp6yr == 2013] <- df$year_lp6yr[df$year_lp6yr == 2013] - 1
```

###COUNT # ROWS WE CHANGED
```{r}
nrow(df[df$recentseason == "Fall",] )
table(df$year_lp6yr == year(df$datelp6), useNA = "ifany")
```

###Create max year - for 2009+ data
```{r}
df$max_year <- pmax(df$year_lp6yr, df$year_ordyr)
```

###convert lpuryear to full year
```{r}
df$lpuryear[df$lpuryear == 3] = 2003
df$lpuryear[df$lpuryear == 4] = 2004
df$lpuryear[df$lpuryear == 5] = 2005
df$lpuryear[df$lpuryear == 6] = 2006
df$lpuryear[df$lpuryear == 7] = 2007
df$lpuryear[df$lpuryear == 8] = 2008
df$lpuryear[df$lpuryear == 9] = 2009
df$lpuryear[df$lpuryear == 0] = 2010
df$lpuryear[df$lpuryear == 1] = 2011
df$lpuryear[df$lpuryear == 2] = 2012
```

###COUNT DISCREPANCY
```{r}
table(df$lpuryear == year(df$datelp6), useNA = "ifany")
```


###Create year - for 2009- data
```{r}
# recode the rest
df$year = c(rep(NA, nrows(df)))
loc6 <- which(as.numeric(format(df$datelp6,"%Y")) == df$lpuryear)
df$year[loc6] <- df$lpuryear[loc6]

loc7 <- which(as.numeric(format(df$datelp6,"%Y")) > df$lpuryear)
df$year[loc7] <- as.numeric(format(df$datelp6[loc7],"%Y"))

loc8 <- which(as.numeric(format(df$datelp6,"%Y")) < df$lpuryear)
df$year[loc8] <- as.numeric(format(df$datelp6[loc8],"%Y"))

year.na <- which(is.na(df$lpuryear))
df$year[year.na] <- as.numeric(format(df$datelp6[year.na],"%Y"))

```


```{r}
df$recency_year <- c(rep(NA, nrow(df)))
df$recency_year[df$max_year >= 2009] <- df$max_year[df$max_year >= 2009]
df$recency_year[df$max_year < 2009] <- df$year[df$max_year < 2009]

df$years_since_purchase <- 2012 - df$recency_year
```


###Clean ordhist = falord + sprord
```{r}
ord_adjust <- function(df) {
  for (i in 1:nrow(df)){
    
    if (df$ordhist[i] < (df$falord[i] + df$sprord[i])){
      df$ordhist[i]<-(df$falord[i] + df$sprord[i])
    }
    else if (df$ordhist[i] > (df$falord[i] + df$sprord[i])){
      if(df$recentseason[i] == "Fall"){
        df$falord[i]<- (df$ordhist[i] - df$sprord[i])
      }
      else if (df$recentseason[i] == "Spring"){
        df$sprord[i]<- (df$ordhist[i] - df$falord[i])}
    }
  }
  return(df)
}

df<-ord_adjust(df)
```

###COUNT DISCREPANCY
```{r}
table(df$ordhist == df$falord + df$sprord, useNA = "ifany")
```

###Impute ordyr counts for consistency
```{r}
ord_impute_ordyear <- function(df_in){
  for (i in 1:nrow(df_in)){
     if(df_in$ordtyr[i]==0
        &df_in$ordlyr[i]==0
        &df_in$ord2ago[i]==0
        &df_in$ord3ago[i]==0
        &df_in$ordhist[i]!=0)
    {
      if (df_in$recency_year[i]==2012){
        df_in$ordtyr[i]<-1
      }
      else if (df_in$recency_year[i]==2011){
        df_in$ordlyr[i]<-1
      }
      else if (df_in$recency_year[i]==2010){
        df_in$ord2ago[i]<-1
      }
      else if (df_in$recency_year[i]==2009){
        df_in$ord3ago[i]<-1
      }
     }
    
  }
  return(df_in)
}

df <- ord_impute_ordyear(df)
```

###delete columns
```{r}
names(df)
drops <- c("max_year","year","year_lp6yr","year_ordyr")
df <- df[,!(names(df) %in% drops)]
```

###Interactions
8 different levels of consistency, how they are defined and if we need this many is up for debate but I think this makes sense. They are all mutually exclusive.
```{r}
df$consistent1 <- as.numeric(df$ordtyr > 0 
                                      & df$ordlyr > 0
                                      & df$ord2ago > 0
                                      & df$ord3ago > 0)
df$consistent2 <- as.numeric(df$ordtyr == 0 
                                      & df$ordlyr > 0
                                      & df$ord2ago > 0
                                      & df$ord3ago > 0)
df$consistent3 <- as.numeric(df$ordtyr > 0 
                                      & df$ordlyr > 0
                                      & df$ord2ago > 0
                                      & df$ord3ago == 0)
df$consistent4 <- as.numeric(df$ordtyr > 0 
                                      & df$ordlyr > 0
                                      & df$ord2ago == 0
                                      & df$ord3ago > 0)
df$consistent5 <- as.numeric(df$ordtyr > 0 
                                      & df$ordlyr == 0
                                      & df$ord2ago > 0
                                      & df$ord3ago > 0)
df$consistent6 <- as.numeric(df$ordtyr > 0 
                                      & df$ordlyr > 0
                                      & df$ord2ago == 0
                                      & df$ord3ago == 0)
df$consistent7 <- as.numeric(df$ordtyr == 0 
                                      & df$ordlyr > 0
                                      & df$ord2ago > 0
                                      & df$ord3ago == 0)
df$consistent8 <- as.numeric(df$ordtyr == 0 
                                      & df$ordlyr == 0
                                      & df$ord2ago > 0
                                      & df$ord3ago > 0)
df$consistent9 <- as.numeric(df$ordtyr > 0 
                                      & df$ordlyr == 0
                                      & df$ord2ago > 0
                                      & df$ord3ago == 0)
df$consistent10 <- as.numeric(df$ordtyr == 0 
                                      & df$ordlyr > 0
                                      & df$ord2ago == 0
                                      & df$ord3ago > 0)
df$consistent11 <- as.numeric(df$ordtyr > 0 
                                      & df$ordlyr == 0
                                      & df$ord2ago == 0
                                      & df$ord3ago > 0)

```

###get temporary subset of just relevant variables
```{r}
consistencies <- df[c("consistent1","consistent2","consistent3","consistent4","consistent5","consistent6","consistent7","consistent8","consistent9","consistent10","consistent11")]
```

###convert into single category
```{r}
df$consistencycategory <- factor((as.matrix(consistencies) %*% (1:ncol(consistencies))) + 1, 
         labels = c("Ref","1", "2","3","4","5","6","7","8","9","10","11"))
```


###drop dummy variables now that we have single categorical variable
```{r}
drops <- c("consistent1","consistent2","consistent3","consistent4","consistent5","consistent6","consistent7","consistent8","consistent9","consistent10","consistent11")
df <- df[,!(names(df) %in% drops)]
```

```{r}
write.csv(df, "cleandata.csv")
```









