---
title: "Logistic Regression"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
#install.packages("tidyverse")
library(tidyverse)
library(lubridate)
```

###load all data from csv in working directory
```{r}
df <- read_csv("cleandata.csv")
```

###to do: impute values for lpuryr
```{r}
table(df$lpuryear, df$recency_year, useNA = "ifany")
df$lpuryear[is.na(df$lpuryear) == TRUE] <- df$recency_year[is.na(df$lpuryear) == TRUE]
```

```{r}
table(df$consistencycategory)
df$consistencycategory <- relevel(factor(df$consistencycategory), 'Ref')
```

#create new column to predict called buy
```{r}
head(df)
df$buy <- 0
df$buy[df$targdol > 0] <- 1
table(df$buy, useNA = "ifany")

#9.4% buy rate
sum(df$buy)/nrow(df)

df[df$buy == 1,]
```

###frequency tables/logistic transform plot (see pg 131 of book)
```{r}
frequency_table <- function(predictor, name) {
  tab <- as.data.frame.matrix(table(predictor, df$buy))
  tab$buy_prop <- tab[,2]/rowSums(tab)
  tab$log_odds <- log(tab$buy_prop/(1 - tab$buy_prop))
  return (plot(x = as.numeric(rownames(tab)), 
               y = tab$log_odds,
               xlab = name,
               ylab = 'log odds'))
}
  
par(mfrow = c(2, 2))
frequency_table(year(df$datead6), 'datead6')
frequency_table(year(df$datelp6), 'datelp6')
frequency_table(df$lpuryear, 'lpuryear')

par(mfrow = c(2, 3))
frequency_table(df$slstyr, 'slstyr')
frequency_table(df$slslyr, 'slslyr')
frequency_table(df$sls2ago, 'sls2ago')
frequency_table(df$sls3ago, 'sls3ago')
frequency_table(df$slshist, 'slshist')

par(mfrow = c(2, 3))
frequency_table(df$ordtyr, 'ordtyr')
frequency_table(df$ordlyr, 'ordlyr')
frequency_table(df$ord2ago, 'ord2ago')
frequency_table(df$ord3ago, 'ord3ago')
frequency_table(df$ordhist, 'ordhist')

par(mfrow = c(2, 2))
frequency_table(df$falord, 'falord')
frequency_table(df$sprord, 'sprord')
frequency_table(df$years_since_purchase, 'years_since_purchase')
```


###split into test and train + other data cleaning
```{r}
df_train <- df[df$train == 1, ]
df_test <- df[df$train == 0, ]

cat('\nActual targdol of test buyers', sum(df_test$targdol))

# #get names
# z <- NULL
# for (name in names(df_test)) {
#   z <- paste(z, name, "+")
# }
# z
```

###nominal logistic regression model?
###fit with glm
```{r}
fit_glm <- glm(buy ~ datead6 + datelp6 + lpuryear + slstyr + slslyr + sls2ago + sls3ago + slshist + ordtyr + ordlyr + ord2ago + ord3ago + falord + sprord + recentseason + years_since_purchase + consistencycategory, 
           family = binomial(link = 'logit'), 
           data = df_train)
summary(fit_glm)
```

###compare predicted to test for first fit
```{r}
test_predict <- predict(fit_glm, newdata = df_test, type = 'response')
table(df_test$buy, round(test_predict, 1), dnn = c('true', 'predicted'))

test_predict[test_predict < .1] <- 0 
test_predict[test_predict >= .1] <- 1 

tab <- table(df_test$buy, test_predict, dnn = c('true', 'predicted'))
tab
cat('CCR:', sum(diag(tab))/sum(tab))
cat('\nTrue targdol of predicted buyers', sum(df_test$targdol[test_predict == 1]))
```

###fit with glm, fewer predictors
```{r}
fit2_glm <- glm(buy ~ datead6 + datelp6 + lpuryear + slshist + ordtyr + falord + sprord + recentseason + years_since_purchase + consistencycategory, 
           family = binomial(link = 'logit'), 
           data = df_train)
summary(fit2_glm)
```

###compare predicted to test for second fit
```{r}
test_predict <- predict(fit2_glm, newdata = df_test, type = 'response')
table(df_test$buy, round(test_predict, 1), dnn = c('true', 'predicted'))

test_predict[test_predict < .1] <- 0 
test_predict[test_predict >= .1] <- 1 

tab <- table(df_test$buy, test_predict, dnn = c('true', 'predicted'))
tab
cat('CCR:', sum(diag(tab))/sum(tab))
cat('\nTrue targdol of predicted buyers', sum(df_test$targdol[test_predict == 1]))
```

###mlogit giving weird singluarity issues
```{r}
# install.packages('mlogit')
# library(mlogit)
# df_reshape <- mlogit.data(data = df, choice = "buy", shape = "wide")
# 
# df_train <- df_reshape[df_reshape$train == 1, ]
# df_test <- df_reshape[df_reshape$train == 0, ]
# 
# df2 <- df[, c('buy', 'years_since_purchase', 'consistencycategory')]
# df3 <- mlogit.data(data = df2, choice = "buy", shape = "wide")
# 
# #get names
# z <- NULL 
# for (name in names(df_test)) {
#   z <- paste(z, name, "+")
# }
# z
# 
# #X1 + targdol + datead6 + datelp6 + lpuryear + slstyr + slslyr + sls2ago + sls3ago + slshist + ordtyr + ordlyr + ord2ago + ord3ago + ordhist + falord + sprord + train + recentseason + recency_year + years_since_purchase + consistencycategory + buy + chid + alt
# 
# fit <- mlogit(buy ~ years_since_purchase + consistencycategory, data = df3)
# 
# 
# #fit <- mlogit(buy ~  datelp6 + slstyr + slslyr + sls2ago + sls3ago + slshist + ordtyr + ordlyr + ord2ago + ord3ago + ordhist + falord + sprord + years_since_purchase + consistencycategory, data = df_train)
# summary(fit)

```
















